HTW E3

### 2024-03-13 Analysis/e3.qmd
tweak e3 plot

pid_slopes3 <- re |>  
    mutate(id=reorder(id,slope)) |>
  ggplot(aes(y=id, x=slope,fill=condit,color=condit)) + 
    geom_pointrange(aes(xmin=Q2.5+adjust, xmax=Q97.5+adjust)) + 
    theme(legend.title=element_blank()) + 
    labs(x="Estimated Slope", y="Participant")  + 
    ggh4x::facet_wrap2(bandOrder~condit,axes="all",scales="free_y")

>>>>

pid_slopes3 <- re |>  
    mutate(id=reorder(id,slope)) |>
  ggplot(aes(y=id, x=slope,fill=condit,color=condit)) + 
    geom_pointrange(aes(xmin=Q2.5+adjust, xmax=Q97.5+adjust)) + 
    theme(legend.title=element_blank()) + 
    labs(x="Estimated Slope", y="Participant")  + 
    ggh4x::facet_nested_wrap(bandOrder~condit,axes="all",scales="free_y")
